---
title: "resig-global"
output: word_document
date: '2022-07-08'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 install/load pkgs

```{r warning=FALSE, message=FALSE}
#install.packages(c("ggplot2", "dplyr", "tidyverse"))
lapply(c("ggplot2",  "tidyverse", "dplyr"), require, character.only = TRUE)
```

## Note
working age population 
OECD: 15 to 64

prime-working-age population 
US: 25 to 54

Age group difference,  young workers usually have higher unemployment
To control the effects, I set age group 20/25 +

Can't find labor force participation rate by ethnicity

# labor force participation rate, 2020-2021 annual, age 25-54

```{r message=FALSE, warning=FALSE}
library(readr)
# Read data, OECD lfpr data by gender
oecd_lfpr_m <- as_tibble(read.csv("~/Desktop/great resignation/OECD datasets/lfpr men 25-54.csv"))
oecd_lfpr_w <- as_tibble(read.csv("~/Desktop/great resignation/OECD datasets/lfpr women 25-54.csv"))
```


```{r}
# OECD lfpr by gender 2020-2021 annual, age 25-54
## subset data
o_l_m <- oecd_lfpr_m %>% filter(Time >2018) %>% select(Country, Time, Value) %>% filter(Country %in% c("United States","Canada", "United Kingdom","Germany", "France", "Italy", "Spain", "Netherlands", "Switzerland", "Sweden", "Belgium", "Ireland", "Norway", "Denmark", "Finland"))

o_l_w <-oecd_lfpr_w %>% filter(Time >2018) %>% select(Country, Time, Value)  %>% filter(Country %in% c("United States","Canada", "United Kingdom","Germany", "France", "Italy", "Spain", "Netherlands", "Switzerland", "Sweden", "Belgium", "Ireland", "Norway", "Denmark", "Finland"))

## only include US, Canada, Germany, France, United Kingdom, Italy, Spain, Netherlands, Switzerland, Sweden, Poland, Belgium, Austria, Ireland, Norway, Denmark, Finland, United States, Canada, Australia, New Zealand

## or exclude countries: Australia, Czech, Japan, Korea, Mexico, New Zealand, Slovak, Turky, OECD, Israel, Chile, Slovenia, Estonia, Lithuania, Latvia, columbia, Costa Rica

```


```{r}
library(ggplot2)
library(viridis)
#install.packages("hrbrthemes")
library(hrbrthemes)
```

### men plot
```{r}
# MALE
o_l_m$Time <- as.factor(o_l_m$Time) # convert integer to factor
plot.men.labor <-ggplot(o_l_m, aes(x=Time, y=Value, fill= Time)) +
  geom_bar(position = "dodge", stat = "identity", width = 0.6) +
  ggtitle("men age 25-54 labor force participation rate") +
  scale_fill_viridis(discrete = T, option = "E") +
  facet_wrap(~Country, nrow = 3, ncol = 5) +
  theme_bw() +
  theme(legend.position="none") +
  xlab("Year")+
  ylab("Labor force participation rate")+
  coord_flip(ylim = c(85, 100))
plot.men.labor
```
#### comment:
In general, men's lfprs are above 85. Switzerland has the highest men's lfprs, around 95.
some countries' lfprs in 2021 are higher than of that in 2020 even 2019. But Germany, Italy, UK, US, Spain, Finland, Ireland are lower than it in 2019.

notes: other factor, migrant labor. lower participation. US, Spain, Italy.
look migrant labor dependence. Eurostats migrant flows.  childcare provision Netherlands (private, vouchers), market of childcare increased, opening of private childcare centers. Germany(local government), public support on childcare. modality, the ways of childcare provision.

### women plot
```{r}
# FEMALE
o_l_w$Time <- as.factor(o_l_w$Time) # convert integer to factor
plot.women.labor <- ggplot(o_l_w, aes(x=Time, y=Value, fill= Time)) +
  geom_bar(position = "dodge", stat = "identity",  width = 0.6) +
  ggtitle("women age 25-54 labor force participation rate") +
  scale_fill_viridis(discrete = T, option = "E") +
  facet_wrap(~Country, nrow = 3, ncol = 5) +
  theme_bw() +
  theme(legend.position="none") +
  xlab("Year")+
  ylab("Labor force participation rate")+
  coord_flip(ylim = c(60, 90))
plot.women.labor
```
#### comment:
All women's lfprs are below 90. Sweden, Switzerland, Finland are higher than 85. Italy has the lowest, between 65-70. US, Switzerland, Germany, and Italy's rates in 2021 are lower than in 2019.

### gender comparison plot 
```{r}
#merge men and women data
o_l_all <- merge(o_l_m, o_l_w, by=c("Country", "Time"))
names(o_l_all)[3] <- 'men'
names(o_l_all)[4] <- 'women'

#install.packages("reshape2")
library(reshape2)
o_l_all_m <- melt(o_l_all, id.vars = c('Country', 'Time'))
names(o_l_all_m)[3] <- 'gender'
```

```{r}
# gender comparison
o_l_all_m$Time <- as.factor(o_l_m$Time) # convert integer to factor
ggplot(o_l_all_m, aes(x=Time, y=value, fill= gender)) +
  geom_bar(position = "dodge", stat = "identity", width = 0.6) +
  ggtitle("age 25-54 labor force participation rate") +
  scale_fill_manual(values = c("men"="cornflowerblue", "women"="coral"))+ 
  facet_wrap(~Country, nrow = 3, ncol = 5) +
  theme_bw() +
  theme(legend.title = element_blank()) +
  xlab("Year")+
  ylab("Labor force participation rate")+
  coord_flip(ylim = c(50, 100))
```
#### comment:
Women's lfprs are generally lower than men's. Italy has the largest gender gap, then US, Ireland.


## other age: labor force participation rate, age 15-64 working age population
comment: the lfpr of population age 15-64 is generally lower than that of age 25-54
```{r}
# read oecd data 15-64 lfpr

oecd_lfpr_m1 <- as_tibble(read.csv("~/Desktop/great resignation/OECD datasets/lfpr men 15-64.csv"))
oecd_lfpr_w1 <- as_tibble(read.csv("~/Desktop/great resignation/OECD datasets/lfpr women 15-64.csv"))

# select countries
o_l_m1 <- oecd_lfpr_m1 %>% filter(Time >2018) %>% select(Country, Time, Value) %>% filter(Country %in% c("United States","Canada", "United Kingdom","Germany", "France", "Italy", "Spain", "Netherlands", "Switzerland", "Sweden", "Belgium", "Ireland", "Norway", "Denmark", "Finland"))

o_l_w1 <-oecd_lfpr_w1 %>% filter(Time >2018) %>% select(Country, Time, Value)  %>% filter(Country %in% c("United States","Canada", "United Kingdom","Germany", "France", "Italy", "Spain", "Netherlands", "Switzerland", "Sweden", "Belgium", "Ireland", "Norway", "Denmark", "Finland"))

# merge data
o_l_all1 <- merge(o_l_m1, o_l_w1, by=c("Country", "Time"))
names(o_l_all1)[3] <- 'men'
names(o_l_all1)[4] <- 'women'

o_l_all_m1 <- melt(o_l_all1, id.vars = c('Country', 'Time'))
names(o_l_all_m1)[3] <- 'gender'
```

###plot1

```{r}
# gender comparison
o_l_all_m1$Time <- as.factor(o_l_m1$Time) # convert integer to factor
ggplot(o_l_all_m1, aes(x=Time, y=value, fill= gender)) +
  geom_bar(position = "dodge", stat = "identity", width = 0.6) +
  ggtitle("age 15-64 labor force participation rate") +
  scale_fill_manual(values = c("men"="cornflowerblue", "women"="coral"))+ 
  facet_wrap(~Country, nrow = 3, ncol = 5) +
  theme_bw() +
  theme(legend.title = element_blank()) +
  xlab("Year")+
  ylab("Labor force participation rate")+
  coord_flip(ylim = c(50, 100))
```

###plot2
```{r}
# gender comparison
o_l_all1$Time <- as.numeric(o_l_all1$Time) # convert to numeric

ggplot(o_l_all1, aes(x=Time)) +
  geom_line(aes(y=men), color = "cornflowerblue")+
  geom_line(aes(y=women), color = "coral") +
  ggtitle("age 15-64 labor force participation rate") +
  facet_wrap(~Country, nrow = 3, ncol = 5) +
  theme_bw() +
  theme(legend.title = element_blank()) +
  xlab("Year")+
  ylab("Labor force participation rate")

```
# net child cost
definitions:
https://data.oecd.org/benwage/net-childcare-costs.htm

This indicator measures the net childcare costs for parents using full-time centre-based childcare, after any benefits designed to reduce the gross childcare fees. Childcare benefits can be received in the form of childcare allowances, tax concessions, fee rebates and increases in other benefit entitlements. Net childcare costs are calculated for both couples and lone parents assuming two children aged 2 and 3. For couples, one parent earns 67% of the average wage whereas the other earns either minimum wage, 67% or 100% of the average wage.


```{r}
# 67 average
oecd_chdcost <- as_tibble(read.csv("~/Desktop/great resignation/OECD datasets/net childcare cost 67average 2004-2021.csv")) 

oecd_chdcost_sub <- oecd_chdcost %>% select(LOCATION, TIME, Value) %>% filter(LOCATION %in% c("USA","CAN", "GBR","DEU", "FRA", "ITA", "ESP", "NLD", "CHE", "SWE", "BEL", "IRL", "NOR", "DNK", "FIN"))

# "United States","Canada", "United Kingdom","Germany", "France", "Italy", "Spain", "Netherlands", "Switzerland (CHE)", "Sweden", "Belgium", "Ireland", "Norway", "Denmark", "Finland"

#rename columns
colnames(oecd_chdcost_sub) <- c('country', 'year', 'childcare_costs')

# replace country names
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'USA'] <- "United States"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'CAN'] <- "Canada"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'GBR'] <- "United Kingdom"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'DEU'] <- "Germany"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'FRA'] <- "France"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'ITA'] <- "Italy"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'ESP'] <- "Spain"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'NLD'] <- "Netherlands"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'CHE'] <- "Switzerland"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'SWE'] <- "Sweden"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'BEL'] <- "Belgium"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'IRL'] <- "Ireland"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'NOR'] <- "Norway"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'DNK'] <- "Denmark"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'FIN'] <- "Finland"
```

### plots
```{r}


# 2004-2021
plot_cost <- ggplot(oecd_chdcost_sub, aes(year, childcare_costs, group = country)) +
  geom_line(aes(color = country))+
  ggtitle("2004-2021 child costs") +
  facet_wrap(~country, nrow = 3, ncol = 5) +
  theme_bw() +
  theme(legend.title = element_blank()) +
  xlab("Year")+
  ylab("Child costs")
plot_cost

# 2018-2021
plot_cost1 <- ggplot(oecd_chdcost_sub[which(oecd_chdcost_sub$year>2017),], aes(year, childcare_costs, group = country)) +
  geom_line(aes(color = country))+
  ggtitle("2018-2021 child costs") +
  facet_wrap(~country, nrow = 3, ncol = 5) +
  theme_bw() +
  theme(legend.title = element_blank()) +
  xlab("Year")+
  ylab("Child costs")
plot_cost1
```

### Notes

Germany's child costs have remained high (above 25) from 2018 to 2021

Nordic countries' child costs have remained low (below 20)  from 2018 to 2021

Before COVID, the US has highest child cost level nearly 30, but droped significant since 2020. 15 at 2021


```{r}
# 67 average / household income
oecd_chdincome <- as_tibble(read.csv("~/Desktop/great resignation/OECD datasets/net childcare 67average_income 2004-2021.csv")) 

oecd_chdincome_sub <- oecd_chdincome %>% select(LOCATION, TIME, Value) %>% filter(LOCATION %in% c("USA","CAN", "GBR","DEU", "FRA", "ITA", "ESP", "NLD", "CHE", "SWE", "BEL", "IRL", "NOR", "DNK", "FIN"))

colnames(oecd_chdincome_sub) <- c('country', 'year', 'childcare_costs_percent')


# replace country names
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'USA'] <- "United States"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'CAN'] <- "Canada"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'GBR'] <- "United Kingdom"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'DEU'] <- "Germany"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'FRA'] <- "France"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'ITA'] <- "Italy"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'ESP'] <- "Spain"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'NLD'] <- "Netherlands"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'CHE'] <- "Switzerland"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'SWE'] <- "Sweden"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'BEL'] <- "Belgium"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'IRL'] <- "Ireland"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'NOR'] <- "Norway"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'DNK'] <- "Denmark"
oecd_chdcost_sub$country[oecd_chdcost_sub$country == 'FIN'] <- "Finland"

```

same as the previous net childcare costs
```{r}
# 2018-2021
plot_income1 <- ggplot(oecd_chdincome_sub[which(oecd_chdincome_sub$year>2017),], aes(year, childcare_costs_percent, group = country)) +
  geom_line(aes(color = country))+
  ggtitle("2018-2021 child costs as percentage of household income") +
  facet_wrap(~country, nrow = 3, ncol = 5) +
  theme_bw() +
  theme(legend.title = element_blank()) +
  xlab("Year")+
  ylab("Child costs percent of income")

plot_income1

```

# Financial disincentive to enter employment with childcare costs

https://data.oecd.org/benwage/financial-disincentive-to-enter-employment-with-childcare-costs.htm#indicator-chart

This indicator measures the percentage of earnings lost to either higher taxes or lower benefits when a parent of two children takes up full-time employment and uses centre-based childcare. Calculations refer to a couple with two children aged 2 and 3 where the other parent works full-time at 67% of the average wage.

```{r}
disincent <- as_tibble(read.csv("~/Desktop/great resignation/OECD datasets/financial disincent with childcare costs.csv"))

disincent_sub <- disincent %>%  select(LOCATION, TIME, Value) %>% filter(LOCATION %in% c("USA","CAN", "GBR","DEU", "FRA", "ITA", "ESP", "NLD", "CHE", "SWE", "BEL", "IRL", "NOR", "DNK", "FIN"))

colnames(disincent_sub) <- c('country', 'year', 'disincentive')

disincent_sub$country[disincent_sub$country == 'USA'] <- "United States"
disincent_sub$country[disincent_sub$country == 'CAN'] <- "Canada"
disincent_sub$country[disincent_sub$country == 'GBR'] <- "United Kingdom"
disincent_sub$country[disincent_sub$country == 'DEU'] <- "Germany"
disincent_sub$country[disincent_sub$country == 'FRA'] <- "France"
disincent_sub$country[disincent_sub$country == 'ITA'] <- "Italy"
disincent_sub$country[disincent_sub$country == 'ESP'] <- "Spain"
disincent_sub$country[disincent_sub$country == 'NLD'] <- "Netherlands"
disincent_sub$country[disincent_sub$country == 'CHE'] <- "Switzerland"
disincent_sub$country[disincent_sub$country == 'SWE'] <- "Sweden"
disincent_sub$country[disincent_sub$country == 'BEL'] <- "Belgium"
disincent_sub$country[disincent_sub$country == 'IRL'] <- "Ireland"
disincent_sub$country[disincent_sub$country == 'NOR'] <- "Norway"
disincent_sub$country[disincent_sub$country == 'DNK'] <- "Denmark"
disincent_sub$country[disincent_sub$country == 'FIN'] <- "Finland"
```

### plot
```{r}
plot_disincent1 <- ggplot(disincent_sub[which(disincent_sub$year>2017),], aes(year, disincentive, group = country)) +
  geom_line(aes(color = country))+
  ggtitle("2018-2021 Financial disincentive to enter employment with childcare costs") +
  facet_wrap(~country, nrow = 3, ncol = 5) +
  theme_bw() +
  theme(legend.title = element_blank()) +
  xlab("Year")+
  ylab("Financial disincentive")

plot_disincent1
```

### Notes:
Canada, Denmark, and the US financial disincentive are over 80, higher than other European countries.
Sweden, Norway, Spain, and Italy are below 80, lower than other European countries.



# Job leavers & starters
Eurostat
report:
https://ec.europa.eu/eurostat/web/products-eurostat-news/-/ddn-20200422-2
database:
https://ec.europa.eu/eurostat/web/lfs/data/database

I choose two datasets:
two age groups: 20-64, 15-74. I choose 20-64 due to childcare considerations

1. Recent job leavers by sex and age 2018 Q1-2022 Q2 quarterly, seasonally adjusted
https://ec.europa.eu/eurostat/databrowser/view/LFSI_LEA_Q__custom_3611506/default/table?lang=en
Recent job leavers are those persons who report to have left their job in the last 3 months before the interview


2. Recent job starters by sex and age 2018 Q1-2022 Q2 quarterly, seasonally adjusted
https://ec.europa.eu/eurostat/databrowser/view/LFSI_STA_Q__custom_3621184/default/table?lang=en
Recent job starters are those persons who have started their employment in the last 3 months before the interview.


```{r}
library("readxl")
```

```{r}
# job leavers 2018-2022
leave_t <- read_excel("~/Desktop/great resignation/eurostat/new/2018-2022 job leave total.xlsx", sheet = 3)
```


```{r}
#clean data and organize data structure
tt <- leave_t [10:46,1:34]
tt <- tt[-2,] 
tt <- tt [, c(1, 2,4, 6, 8, 10, 12, 14, 16, 18, 20, 22, 24, 26, 28, 30, 32, 34)] # 2018 Q1-2022 Q1 data
```

```{r}
#create lists for variables
time <- as.list(tt[1,])
time[[1]]=NULL
bel<- as.list(tt[2,])
bel[[1]]=NULL
den <- as.list(tt[5,])
den[[1]]=NULL
ger <- as.list(tt[6,])
ger[[1]]=NULL
ire <- as.list(tt[8,])
ire[[1]]=NULL
gree <- as.list(tt[9,])
gree[[1]]=NULL
spa <- as.list(tt[10,])
spa[[1]]=NULL
ita <- as.list(tt[13,])
ita[[1]]=NULL
neth <- as.list(tt[20,])
neth[[1]]=NULL
fin <- as.list(tt[27,])
fin[[1]]=NULL
swed <- as.list(tt[28,])
swed[[1]]=NULL
ice <- as.list(tt[29,])
ice[[1]]=NULL
norw <- as.list(tt[30,])
norw[[1]]=NULL
switz <- as.list(tt[31,])
switz[[1]]=NULL
uk <- as.list(tt[32,])
uk[[1]]=NULL
```


```{r}
# repeat 17 times country name for each country
n <- 17 # 17 for 2018 Q1-2022 Q1
Belgium <- as.list(rep("Belgium",n))
Denmark <- as.list(rep("Denmark",n))
Germany <- as.list(rep("Germany",n))
Ireland <- as.list(rep("Ireland",n))
Greece <- as.list(rep("Greece",n))
Spain <- as.list(rep("Spain",n))
Italy <- as.list(rep("Italy",n))
Netherlands <- as.list(rep("Netherlands",n))
Finland <- as.list(rep("Finland",n))
Sweden <- as.list(rep("Sweden",n))
Iceland <- as.list(rep("Iceland",n))
Norway  <- as.list(rep("Norway",n))
Switzerland <- as.list(rep("Switzerland",n))
United_Kingdom <- as.list(rep("United Kingdom",n))
```


```{r}
#combine all country lists
# country columns
countrybel <- c("Country", Belgium)
country <- c(countrybel,Denmark,Germany,Ireland,Greece,Spain,Italy,Netherlands,Finland,Sweden,Iceland,Norway,Switzerland,United_Kingdom)
```


```{r}
#combine all values
# values columns
values <- c(bel,den,ger,ire,gree,spa,ita,neth,fin,swed,ice,norw,switz,uk)
values_all <- c("Values", values)
```


```{r}
# time column
# repeat for 14 countries
n1=14
time_rep <- rep(time, n1)
time_all <- c("Time", time_rep)
```


```{r}
# transpose columns to rows
country1 <- t(as.data.frame(country))
time1 <- t(as.data.frame(time_all))
values1 <- t(as.data.frame(values_all))
```


```{r}
# combine all
leaveall <- as.data.frame(cbind(country1, time1, values1))
# rename columns
colnames(leaveall)[1] <- "Country"
colnames(leaveall)[2] <- "Time"
colnames(leaveall)[3] <- "Values"
leaveall[-1,]
```
```{r}
# export data
# write.csv(leaveall,"~/Desktop/great resignation/eurostat/new/leaveall.csv", row.names = FALSE)
```


```{r}
leave_m <- read_excel("~/Desktop/great resignation/eurostat/new/2018-2022 job leave sex.xlsx", sheet = 3)
leave_w <- read_excel("~/Desktop/great resignation/eurostat/new/2018-2022 job leave sex.xlsx", sheet = 4)
```

clean male and female datasets
```{r}
# males
```


```{r}
# females
```

# china
```{r}
china <- read_excel("~/Desktop/great resignation/china/turnover.xlsx")
```


